\newpage
\pagenumbering{roman}
\newpage
\section*{Declaration}
\noindent I Osamai Osbert do declare to the best of my knowledge that the information presented in this report is original and my own work and effort and has never been submitted to any college, institution or University for any form of award whatsoever.
\newline
\newline
\newline
\newline
\noindent Signed.................................      Date...................................
\newline
\noindent Osamai Osbert
\pagestyle{plain}
\addcontentsline{toc}{section}{Declaration}
\noindent
\newpage
\section*{Approval}
\noindent This project report has been submitted with my approval as supervisor.
\newline
\newline
\newline
\newline
\noindent Signed.................................      Date...................................
\newline
\noindent Dr. Benjamin Kanagwa, PhD
\newline
\noindent Department of Networks,
\newline
\noindent School of Computing and Information Technology,
\newline
\noindent Makerere University.
\pagestyle{plain}
\addcontentsline{toc}{section}{Approval}
\noindent
\newpage
\section*{Dedication}
\noindent This work is dedicated to the men and women of the Uganda Police who tirelessly serve and protect our nation.
\newline
\newline
\pagestyle{plain}
\addcontentsline{toc}{section}{Dedication}
\noindent
\newpage
\noindent
\newpage
\section*{Acknowledgement}
\noindent I would like to thank and appreciate all those who contributed time and effort towards this report. Special thanks go to my supervisor Dr. Benjamin Kanagwa for every support accorded to me in completing this project. 
\newline
I am greatly indebted to my family (My wife Lucy, daughter Alba, sisters Kevine and Suzan and brothers Euphrasius and Godfrey) for all the support and encouragement they offered throughout the course.
I also express my gratitude to my workmates at Tropical Bank Uganda especially Mr. Nicholas Ssesinde for the morale and encouragement they provided me during this course.
\newline
\noindent May the Almighty God reward them abundantly.
\newline
\newline
\pagestyle{plain}
\addcontentsline{toc}{section}{Acknowledgement}
\noindent
\newpage
\section*{LIST OF ACRONYMS}
\pagestyle{plain}
\addcontentsline{toc}{section}{Acronyms}
\begin{tabular}{lll}
{\bf EJB }&~~~~~~~~~~~~~~ 	        Enterprise Java Beans\\
{\bf SOA}&~~~~~~~~~~~~~~                Service Oriented Architecture\\
{\bf CEP}&~~~~~~~~~~~~~~ 		Complex Event Processing \\
{\bf XHTML}&~~~~~~~~~~~~~~              Extensible HyperText Markup Language  \\
{\bf JPA}&~~~~~~~~~~~~~~               	Java Persistence API\\
{\bf EIS}&~~~~~~~~~~~~~~ 		Extended Information Server\\
{\bf PDF}&~~~~~~~~~~~~~~ 		Portable Document Format\\
{\bf IEEE}&~~~~~~~~~~~~~~ 	        Institute of Electrical and Electronic Engineers\\ 
{\bf EL}&~~~~~~~~~~~~~~ 		Expression Language \\
{\bf HTML}&~~~~~~~~~~~~~~ 		HyperText Markup Language\\
{\bf SNA}&~~~~~~~~~~~~~~ 		Social Network Analysis\\
{\bf GIS}&~~~~~~~~~~~~~~ 		Geographic Information System\\
{\bf SPP}&~~~~~~~~~~~~~~ 	        Spatial Point Patterns\\
{\bf AMIT}&~~~~~~~~~~~~~~ 		Active Middleware Technology\\
{\bf GPL}&~~~~~~~~~~~~~~ 		General Public License\\
{\bf SQL }&~~~~~~~~~~~~~~ 		Structured Query Language\\
{\bf ECA}&~~~~~~~~~~~~~~ 		Event Condition Action\\
{\bf POJO}&~~~~~~~~~~~~~~ 		Plain Old Java Object\\
{\bf EPL}&~~~~~~~~~~~~~~ 	        Event Processing Language\\
{\bf SDLC}&~~~~~~~~~~~~~~ 	        System Development Life Cycle\\
{\bf UML}&~~~~~~~~~~~~~~ 	        Unified Modeling Language\\
{\bf JSF}&~~~~~~~~~~~~~~ 	        Java Server Faces\\
{\bf Java EE}&~~~~~~~~~~~~~~ 	        Java Enterprise Edition\\
{\bf CEL}&~~~~~~~~~~~~~~ 	        Cayuga Event Language\\
{\bf ESBs}&~~~~~~~~~~~~~~ 	        Event Service Buses\\
{\bf ICT}&~~~~~~~~~~~~~~ 	        Information and Communication Technology\\
{\bf CCTV}&~~~~~~~~~~~~~~ 	        Closed-Circuit Television\\
{\bf GPL}&~~~~~~~~~~~~~~ 	        General Public License\\
{\bf API}&~~~~~~~~~~~~~~ 	        Application Programming Interface\\

\end{tabular}

\newpage
\section*{Abstract}
\noindent Crime investigation world over is considered a difficult and laborious process that heavily relies on efficient crime analysis to ensure accurate and timely conclusions. This is not helped by the fact that law enforcement agencies deploy manual investigation processes and computerized systems that cannot quickly identify complex crime patterns.In Uganda, the situation is no different with these agencies facing massive delays in crime solving and increasing numbers of sophisticated crimes, most of them of the organized category. Every year tens of thousands of cases are carried forward to the following year, uncompleted.Majority of these crimes evolve in a long period of time making them even more difficult to predict. 
\noindent Criminals have become very intelligent due to the advancement of technology and therefore they conduct crimes in an untraceable manner. Intelligence and law enforcement agencies are often faced with the dilemma of having too much data, which in effect makes too little value and the lack of sophisticated network analysis tools and techniques to utilize the data effectively and efficiently. 
\noindent In this project the phenomenon of Complex Event Processing (CEP) is used to detect patterns in crime related events using a CEP engine for high throughput and performance. CEP analyses low level events to produce a single complex event and has been successfully used in Stock Trading, Network Analysis and other areas. CEP uses a collection tools and techniques()to detect pre-defined patterns/rules in data streams. The patterns are created as queries using query languages and are stored instead of storing data as is the case with databases. Because of this design,the tool will enable quick processing and analysis of crime data and also provide a basis for unearthing emerging patterns.
\newline
\pagestyle{plain}
\addcontentsline{toc}{section}{Abstract}
\newpage
\tableofcontents
