
\begin{center}
{\bf \Large A CRIME INVESTIGATION TOOL BASED ON EVENT PATTERN DETECTION :\newline }\vspace{1cm} \\
 {\bf by}\\ {\bf Osbert Osamai  }\\
{\bf Reg. No: 2010/HD18/1259U}\\
{\bf BITC (KYU)}
 \\
{\bf Department of Networks}\\
{\bf School of Computing and Informatics Technology, Makerere University}\\ E-mail: omeja4ever@gmail.com,oosbert@trobank.com \\Tel: +256712738530
\vspace{2cm}\\

{\bf A Project Report Submitted to the School of Graduate Studies in Partial Fulfillment for the Award of Master of Science in Data Communication and Software Engineering Degree of Makerere University.}\\ 
{\bf OPTION: Mobile Computing} 
\vspace{1cm}\\ 
{\bf Supervisor}
\\{\bf Kanagwa Benjamin (PhD)}\\{Signature ------------------------}\\{Date   --------------------------}\\{\bf Department of Networks}\\
{\bf School of Computing and Information Technology, Makerere University}\\ Email:
bkanagwa@gmail.com  Tel: +256-712495020   \vspace{2cm}\\


{\bf March 2013 }
\end{center}

\input setbmp
\makeatletter
    \def\thebibliography#1{\section*{References\@mkboth
      {REFERENCES}{REFERENCES}}\list
      {[\arabic{enumi}]}{\settowidth\labelwidth{[#1]}\leftmargin\labelwidth
	\advance\leftmargin\labelsep
	\usecounter{enumi}}
	\def\newblock{\hskip .11em plus .33em minus .07em}
	\sloppy\clubpenalty4000\widowpenalty4000
	\sfcode`\.=1000\relax}
    \makeatother
\newtheorem{defn}{Definition}[section]
\newcommand{\ud}{\underline}
\newcommand{\vs}{{\vspace{4.6mm}}}
\pagestyle{empty}
\linespread{2}

\newpage
\tableofcontents
\newpage
\section*{Declaration}


{I Osamai Osbert, declare that this report is my original work and has never been published or submitted for any other award to any university/institution
of higher learning.}




\noindent{Signed ------------------------}\\{Date   --------------------------}\\

\noindent{}
{\it Osamai Osbert}

\pagestyle{plain}
\pagenumbering{roman}

\addcontentsline{toc}{section}{Declaration}
\newpage
\section*{Approval}

\noindent{This project report has been submitted with my approval as supervisor}


\noindent{Signed: ............................................. Date:................................................}




\noindent{\bf Dr.Benjamin Kanagwa (PhD)}

\noindent{Department of Networks,}
\noindent{School of Computing and Information Technology,}
\noindent{Makerere University.}


\addcontentsline{toc}{section}{Approval}
\newpage
\section*{Dedication}

\noindent This work is dedicated to the Uganda Police with a plea for transparency and fairness toward the ugandan people.
\addcontentsline{toc}{section}{Dedication}
\newpage
\section*{Acknowledgements}
\addcontentsline{toc}{section}{Acknowledgements}
\noindent I would like to thank Dr. Kanagwa Benjamin my supervisor for the guidance and insightful contribution to this project. I also thank the Uganda Police for the cooperation accorded to me during the requirements gathering period, my colleagues at university and work for the support and my family(Alba,Lucy,Suzan,Kevine,Euphrasius,Godfrey,Peter,Sarah) for all their well intended contributions.
\newpage
\section*{List of Acronyms}
\addcontentsline{toc}{section}{Acronyms}

\begin{tabular}{lll}

{\bf CEP }&~~~~~~~~~~~~~~ 	        Complex Event Processing\\
{\bf SNA}&~~~~~~~~~~~~~~                Social Network Analysis\\
{\bf GIS}&~~~~~~~~~~~~~~ 		Geographical Information Systems \\
{\bf SPP}&~~~~~~~~~~~~~~                Spatial Point Patterns\\
{\bf SQL}&~~~~~~~~~~~~~~                Structured Query Language\\
{\bf SOA}&~~~~~~~~~~~~~~                Service Oriented Architecture\\
{\bf JDBC}&~~~~~~~~~~~~~~               Java Database Connectivity\\
{\bf ODBC}&~~~~~~~~~~~~~~               Open Database Connectivity\\
{\bf SOA}&~~~~~~~~~~~~~~                Service Oriented Architecture\\
{\bf XML}&~~~~~~~~~~~~~~ 		Manipulation Language\\
{\bf CSV}&~~~~~~~~~~~~~~ 		Comma Separated Values\\
{\bf POJO}&~~~~~~~~~~~~~~ 		Plain Old Java Object\\
{\bf SDLC}&~~~~~~~~~~~~~~ 	        System Development Life Cycle\\



\end{tabular}
